Analyzing DECREASE trials for extent of data fabrication

### 2016-07-28 submission/manuscript.Rmd
Minor correction in code.

```{r, echo = FALSE}
suppressPackageStartupMessages(if(!require(metafor)){install.package('metafor')})
suppressPackageStartupMessages(library(metafor))
suppressPackageStartupMessages(if(!require(latex2exp)){install.package('latex2exp')})
suppressPackageStartupMessages(library(latex2exp))

>>>>

```{r, echo = FALSE}
suppressPackageStartupMessages(if(!require(metafor)){install.packages('metafor')})
suppressPackageStartupMessages(library(metafor))
suppressPackageStartupMessages(if(!require(latex2exp)){install.packages('latex2exp')})
suppressPackageStartupMessages(library(latex2exp))
